---
title: "05_visualising"
author: "Astrid Elmann Hansen"
date: '2023-01-06'
output:
  html_document:
    toc: true
    toc_float: true
---

```{r}
pacman::p_load(tidyverse, ggridges)

# loading files
df <- read_csv("data/fv_22_kandidat_test.csv")
ans <- read_csv("data/answers.csv")

# Arranging education levels from lowest to highest
df$education <- factor(df$education,
                  levels = c("Ikke oplyst", 
                             "Grundskole", 
                             "10. klasse",
                             "Gymnasial uddannelse",                             
                             "Erhvervsuddannelse",
                             "Seminaruddannelse",
                             "Bachelor-/diplomuddannelse",
                             "Kandidat-/masteruddannelse",
                             "Ph.d.-uddannelse"
                             ))

# arranging parties according to DRs scale
df$party <- factor(df$party, 
                   levels = c("Q", "Å", "Ø", "F", "B", "A", "M", "V", "C","O", "D", "I", "Æ", "K"))

# string of the colours typically used to represent the (elected) parties.
party_cols <- c("#25772b", "#dd6b16", "#d76698", "#5f206d", "#69171a", "#a475c8", "#1d3151", "#8fa61d", "#ffbd31", "#14696c", "#35a4b0", "#6581c7")

# counting how many candidates participated
df %>% group_by(participated) %>% summarise(n = n())

# counting how many elected candidates participated
df %>% filter(elected == T) %>% group_by(participated) %>% summarise(n = n())
```

# Investigating the candidates
## Looking at education levels

```{r}
df %>% 
  ggplot(aes(x = education, fill = elected)) + 
  geom_bar() +
  coord_flip()
```

```{r}
df %>% filter(education == "Ikke oplyst" |
              education == "Erhvervsuddannelse" |
              #education == "Grundskole" |
              #education == "10. klasse" |
              education == "Gymnasial uddannelse" |
              education == "Seminaruddannelse" |
              #education == "Bachelor-/diplomuddannelse" |
              education == "Kandidat-/masteruddannelse") %>%  #|
              #education == "Ph.d.-uddannelse") %>% 
  ggplot(aes(x = education, fill = elected)) + 
  geom_bar() +
  coord_flip() +
  ggtitle("5 most common education levels among candidates")
```

## Looking at jobs
```{r}
df %>% 
	group_by(profession) %>% 
	summarise(count = n()) %>% 
	ggplot(aes(x = reorder(profession,(-count)), y = count)) + 
	geom_bar(stat = 'identity') +
  coord_flip() 
```


# Is a candidate elected based on...
## ...whether they participated in the candidate test?
```{r}
df %>% ggplot(aes(x = participated, y = elected)) +
  geom_jitter() # who are the three people?
```

## ...a strong conviction when answering questions
```{r}
df %>% 
  ggplot(aes(x = conviction, fill = elected)) +
  geom_density(alpha = 0.5) +
  theme_bw() +
  ggtitle("Density plot of candidates' conviction") +
  labs(x = "Conviction %",
       y = NULL,
       fill = 'Elected') +
  scale_fill_manual(values=c("#999999", "#03ac16"))+
  theme(axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.position = c(0.88, 0.8))
  
ggsave("plots/candidate_convitction.pdf", width=4, height=3, dpi=200)
```
### is this difference significant?
```{r}
elected <- df %>% filter(elected == T & participated == T)
not_elected <- df %>% filter(elected == F & participated == T)
t.test(elected$conviction, not_elected$conviction)

# find data on distributions
mean(elected$conviction)
sd(elected$conviction)

mean(not_elected$conviction)
sd(not_elected$conviction)
```
> It is significant :)


## ...the number of notes?
```{r}
df %>% 
  filter(participated == T) %>% 
  ggplot(aes(x = no_notes, fill = elected)) +
  geom_histogram(bins = 25) +
  theme_bw() +
  ggtitle("Number of notes from all candidates") +
  labs(x = "No of notes",
       y = "Count",
       fill = "Elected") +
  #theme(legend.position="none")+
  scale_fill_manual(values=c("#999999", "#03ac16")) +
  scale_x_continuous(breaks = seq(0,25, by = 1))

ggsave("plots/note_hist.pdf", width=8, height=5, dpi=200)
```

# Do candidates within a party have smiliar levels of conviction?

```{r fig.width = 5, fig.height = 8}
df %>% 
  filter( party != "Q" & party != "K") %>% 
  ggplot(aes(x = conviction, y = party, fill = party)) +
  geom_density_ridges(scale = 3, alpha = 0.8, rel_min_height = 0.045) +
  theme_bw() +
  ggtitle("Density plot of parties' conviction") +
  labs(x = "Conviction %",
       y=NULL,
       fill = 'Party') +
  theme (legend.position="none", 
         axis.text.y = element_text(size=15, face="bold", color = "black"))+
  xlim(0,100) +
  scale_fill_manual(values = party_cols)
  
ggsave("plots/party_convitction.pdf", width=5, height=8, dpi=200)
```

```{r}
df %>% 
  filter( party != "Q" & party != "K" & party != "D") %>% 
  filter(elected == T) %>% 
  ggplot(aes(x = conviction, fill = party)) +
  geom_area(stat = "bin") +
  theme_bw() +
  ggtitle("Histogram of elected candidates' conviction") +
  labs(x = "Conviction %",
       y=NULL,
       fill = 'Party') +
  theme (legend.position="none", 
         axis.text.y = element_text(size=15, face="bold", color = "black"))+
  xlim(0,100) +
  scale_fill_manual(values = party_cols) 
  
#ggsave("plots/elected_convitction.pdf", width=5, height=8, dpi=200)
```

# Is there a connection between amount and length of notes?
```{r}
df %>% 
  filter(participated == T) %>% 
  ggplot(aes(y = avg_note_len, x = no_notes, color = elected, size = elected)) +
  geom_point()+
  theme_bw() +
  ggtitle("Candidates' notes and their election status") +
  labs(y = "Average characters in notes",
       x = "Number of notes",
       size = 'Elected',
       color = "Elected") +
  scale_color_manual(values=c("#999999", "#03ac16")) +
  scale_size_manual(values=c(2,4)) +
  annotate("text", x=5, y=0, label= "114 candidates with 0 notes") 

ggsave("plots/notes.pdf", width=8, height=5, dpi=200)

# find amount of candidates with 0 notes
df %>% 
  filter(participated == T & no_notes == 0) %>% 
  count()
```


# What are the most and least dividing questions?

```{r}
i <- 1
for (q in ans[2:26]){
p <- ans %>% ggplot(aes(x = q)) + 
  geom_histogram() +
  ggtitle(paste0("Q no ", i)) 
i = i+1
print(p)
}
```




